### 2009-09-03 doc/tech_doc/janitor/tex_concept/concept.tex
Janitor documetation fixes: build fixed, tex fixed, image recovered

 \begin{landscape}
\begin{figure}[!h]
\vspace{4cm}
 \begin{center} 
    % \resizebox{24cm}{!}{\input{images/dependencies}}
    \mycaption{Modules of the Janitor and their dependencies}{}
 \end{center} 
\vfill
 \label{fig:janitorDependencies} 
\end{figure}
 \end{landscape}

@@

\begin{table}[!h]
 \begin{center}
 \begin{tabular}{lp{12cm}}
 State&Description\\
 \hline
 UNAVAILABLE&
	The RE is not available for the BaseSystem (see \ref{sec:rdfschema}) the site uses. \\
 INSTALLABLE&
	The RE is available for the BaseSystem the site uses and it
	will be automatically installed once a job requests it. \\
 INSTALLING/a&
	A job requested the RE and it is currently being installed \\
 INSTALLING/m&
	The RE-adminstrator requested the installation of the RE. Its
	currently being installed. \\
 FAILED&
	The installation process failed. \\
 INSTALLED/a&
	The RE is installed dynamically. \\
 INSTALLED/m&
	The RE ist installed manually by the RE-administrator \\
 BROKEN/m&
	The RE is installed but failed tests of the RE-administrator \\
 VALIDATED/m&
	The RE is installed and successfully passed the tests of the
	RE-administrator \\
 REMOVAL PENDING&
	The RE is still installed but will be removed as soon as
	possible. It is not available to new jobs. \\
 REMOVING&
	The RE is currently being removed. \\
 INSTALLED/s&
	The RE was installed in the traditional way by the site administrator. \\
 BROKEN/s&
	The RE was installed in the traditional way and failed
	validation by the RE-administrator, \\
 VALIDATED/s&
	The RE was installed in the traditional way and was
	successfully verified.
 \\
 \end{tabular}
 \end{center}
 \mycaption{States a Runtime Environment can possibly be in.}{}
 \label{tab:states}
 \end{table}

@@

\begin{figure}[!h]
  \begin{center}
    \includegraphics[width=5cm]{images/arex-stages.pdf}
    \mycaption{}{}
    \label{fig:RE_states}
  \end{center}
\end{figure}

\begin{figure}[!h]
  \begin{center}
    \includegraphics[width=12cm]{images/janitor_integration_2nd_edition.pdf}
    \mycaption{}{}
    \label{fig:RE_states}
  \end{center}
\end{figure}

@@

\begin{figure}[!h]
  \begin{center}
    \includegraphics[width=12cm]{images/WS_structure.pdf}
    \mycaption{}{\task{To be translated and beautificated. SVG file is missing!}}
    \label{fig:RE_states}
  \end{center}
\end{figure}

Proposal for SOAP messages:\\
 namespace: dynamicruntime or janitor\\
\task{Create WSDL files for that}
\task{Permission concepts: Depending on certificates. Certain certificates may \texttt{sweep}. Defined in service\_HED.xml. Evaluated in:?? }
\lstsetJUSTXML
\begin{lstlisting}[
        label=lst:SOAPrequest,
        caption={ [Example \textit{arc.conf} settings for janitor.]
                  \textbf{Example \textit{arc.conf} settings for janitor.}}
        ]
<Request action="SEARCH|SWEEP|LIST|DEPLOY|REMOVE|CHECK|REGISTER">
	<Initiator jobid="1234"/>  <!-- Needed for: CHECK|REGISTER|DEPLOY|REMOVE -->
                                  <!-- May contain no jobID in this case a new one will 
                                       be created and returned via the response message-->

@@

\lstsetJUSTXML
\begin{lstlisting}[
        label=lst:SOAPrequest,
        caption={ [Example \textit{arc.conf} settings for janitor.]
                  \textbf{Example \textit{arc.conf} settings for janitor.}}
        ]
<response action="SEARCH|SWEEP|LIST|DEPLOY|REMOVE|CHECK|REGISTER">
	<initiator jobid="1234"/>  <!-- Needed for REMOVE|REGISTER|DEPLOY|CHECK-->
	<result code="0" message="Sucessfully initailized job."> <!-- -->
	<jobs> <!--LIST|CHECK-->
		<job jobid="1234">
			<created>1234567890</created>    <!-- in unix time-->
			<age>0</age>           <!-- in seconds-->
			<runtimeenvironment>
				<package>APPS/BIO/WEKA-3.4.10</package>
			</runtimeenvironment>
			<state>INITIALIZED</state>
		</job>
		<job jobid="4321">
			<created>1234567891</created>
			<age>0</age>
			<package>APPS/BIO/WEKA-3.4.10</package>
			<state>INITIALIZED</state>
			<runtimeenvironmentkey>APPS_BIO_WEKA_3_4_10-835614b62c98c4eb6cb03d74d3161b5d</runtimeenvironmentkey> <!-- at least CHECK -->
			<uses>/nfshome/knowarc/dredesign/src/services/dRE3/perl/spool/runtime/jre__57T1ke1UVz/runtime</uses> <!-- at least CHECK -->
			<uses>/nfshome/knowarc/dredesign/src/services/dRE3/perl/spool/runtime/weka_wHfyytarlE/runtime</uses> <!-- at least CHECK -->
		</job>
	</jobs>

>>>>

 \begin{landscape}
\begin{figure}[!h]
\vspace{4cm}
 \begin{center} 
    %\resizebox{24cm}{!}{\input{images/dependencies}}
    \includegraphics[width=24cm]{images/dependencies.pdf}
    \mycaption{Modules of the Janitor and their dependencies}{}
 \end{center} 
\vfill
 \label{fig:janitorDependencies} 
\end{figure}
 \end{landscape}

@@

\begin{table}[!h]
 \begin{center}
 \begin{tabular}{lp{12cm}}
 State&Description\\
 \hline
 UNAVAILABLE&
	The RE is not available for the BaseSystem (see \ref{sec:catalog}) the site uses. \\
 INSTALLABLE&
	The RE is available for the BaseSystem the site uses and it
	will be automatically installed once a job requests it. \\
 INSTALLING/a&
	A job requested the RE and it is currently being installed \\
 INSTALLING/m&
	The RE-adminstrator requested the installation of the RE. Its
	currently being installed. \\
 FAILED&
	The installation process failed. \\
 INSTALLED/a&
	The RE is installed dynamically. \\
 INSTALLED/m&
	The RE ist installed manually by the RE-administrator \\
 BROKEN/m&
	The RE is installed but failed tests of the RE-administrator \\
 VALIDATED/m&
	The RE is installed and successfully passed the tests of the
	RE-administrator \\
 REMOVAL PENDING&
	The RE is still installed but will be removed as soon as
	possible. It is not available to new jobs. \\
 REMOVING&
	The RE is currently being removed. \\
 INSTALLED/s&
	The RE was installed in the traditional way by the site administrator. \\
 BROKEN/s&
	The RE was installed in the traditional way and failed
	validation by the RE-administrator, \\
 VALIDATED/s&
	The RE was installed in the traditional way and was
	successfully verified.
 \\
 \end{tabular}
 \end{center}
 \mycaption{States a Runtime Environment can possibly be in.}{}
 \label{tab:states}
 \end{table}

@@

\begin{figure}[!h]
  \begin{center}
    \includegraphics[width=5cm]{images/arex-stages.pdf}
    \mycaption{}{}
    \label{fig:arex_states}
  \end{center}
\end{figure}

\begin{figure}[!h]
  \begin{center}
    \includegraphics[width=12cm]{images/janitor_integration_2nd_edition.pdf}
    \mycaption{}{}
    \label{fig:janitor_integration_2}
  \end{center}
\end{figure}

@@

\begin{figure}[!h]
  \begin{center}
    \includegraphics[width=12cm]{images/WS_structure.pdf}
    \mycaption{}{\task{To be translated and beautificated. SVG file is missing!}}
    \label{fig:WS_structure}
  \end{center}
\end{figure}

Proposal for SOAP messages:\\
 namespace: dynamicruntime or janitor\\
\task{Create WSDL files for that}
\task{Permission concepts: Depending on certificates. Certain certificates may \texttt{sweep}. Defined in service\_HED.xml. Evaluated in:?? }
\lstsetJUSTXML
\begin{lstlisting}[
        label=lst:arc_conf2,
        caption={ [Example \textit{arc.conf} settings for janitor.]
                  \textbf{Example \textit{arc.conf} settings for janitor.}}
        ]
<Request action="SEARCH|SWEEP|LIST|DEPLOY|REMOVE|CHECK|REGISTER">
	<Initiator jobid="1234"/>  <!-- Needed for: CHECK|REGISTER|DEPLOY|REMOVE -->
                                  <!-- May contain no jobID in this case a new one will 
                                       be created and returned via the response message-->

@@

\lstsetJUSTXML
\begin{lstlisting}[
        label=lst:arc_conf3,
        caption={ [Example \textit{arc.conf} settings for janitor.]
                  \textbf{Example \textit{arc.conf} settings for janitor.}}
        ]
<response action="SEARCH|SWEEP|LIST|DEPLOY|REMOVE|CHECK|REGISTER">
	<initiator jobid="1234"/>  <!-- Needed for REMOVE|REGISTER|DEPLOY|CHECK-->
	<result code="0" message="Sucessfully initailized job."> <!-- -->
	<jobs> <!--LIST|CHECK-->
		<job jobid="1234">
			<created>1234567890</created>    <!-- in unix time-->
			<age>0</age>           <!-- in seconds-->
			<runtimeenvironment>
				<package>APPS/BIO/WEKA-3.4.10</package>
			</runtimeenvironment>
			<state>INITIALIZED</state>
		</job>
		<job jobid="4321">
			<created>1234567891</created>
			<age>0</age>
			<package>APPS/BIO/WEKA-3.4.10</package>
			<state>INITIALIZED</state>
			<runtimeenvironmentkey>APPS_BIO_WEKA_3_4_10-835614b62c98c4eb6cb03d74d3161b5d</runtimeenvironmentkey> <!-- at least CHECK -->
			<uses>/nfshome/knowarc/dredesign/src/services/dRE3/perl/spool/runtime/jre__57T1ke1UVz/runtime</uses> <!-- at least CHECK -->
			<uses>/nfshome/knowarc/dredesign/src/services/dRE3/perl/spool/runtime/weka_wHfyytarlE/runtime</uses> <!-- at least CHECK -->
		</job>
	</jobs>

### 2009-09-03 doc/tech_doc/janitor/tex_maintenance/maintenance.tex
Janitor documetation fixes: build fixed, tex fixed, image recovered

\section{Introducing new packages}\label{sec:catalog}

@@

The WEKA package for machine learning~\cite{FRANK_20074} and the Java Runtime Environment
are available as dynamic Runtime Environments. Further packages for bioinformatics comprise dynamic
variants of tools for the analysis of transcription factor binding sites. These are already offered for manual
installation via the prior mentioned traditional page representing Runtime Environments for ARC. 
The corresponding tar file is named \task{somewhat??}. The \texttt{data} directory simply contains a ZIP file
which needs to be unzipped in the installation directory. For that reason, the \texttt{control/install} script is 
written as follows:
% dollar signs made trouble in listings *hrmlgrmpf* ... Costs too much time to figure out why *ARC!*
\begin{verbatim} 
#!/bin/sh
set -e  # Makes the script to terminate at the first line it fails.

@@

\section{Typical use cases}\label{sec:catalog}

>>>>

\section{Introducing new packages}\label{sec:introducing_new_packages}

@@

The WEKA package for machine learning~\cite{FRANK_2004} and the Java Runtime Environment
are available as dynamic Runtime Environments. Further packages for bioinformatics comprise dynamic
variants of tools for the analysis of transcription factor binding sites. These are already offered for manual
installation via the prior mentioned traditional page representing Runtime Environments for ARC. 
The corresponding tar file is named \task{somewhat??}. The \texttt{data} directory simply contains a ZIP file
which needs to be unzipped in the installation directory. For that reason, the \texttt{control/install} script is 
written as follows:
% dollar signs made trouble in listings *hrmlgrmpf* ... Costs too much time to figure out why *ARC!*
\begin{verbatim} 
#!/bin/sh
set -e  # Makes the script to terminate at the first line it fails.

@@

\section{Typical use cases}\label{sec:typical_use_cases}

### 2009-09-03 doc/tech_doc/janitor/tex_usage/usage.tex
Janitor documetation fixes: build fixed, tex fixed, image recovered

The Janitor can be used either with or without A-REX. In case A-REX is used, installations will be maintained automatically the runtime environments.

@@

Runtime Environments can be specified using the supported job description languages.
The most representative two common languages shall be explained at this point: xRSL and JSDL.
Listing~\ref{lst:xrsl_job} shows the xRSL example in which two runtime environments are requested.

\lstsetXRSL
\begin{lstlisting}[
        label=lst:xrsl_job,
        caption={ [Job submission using the xRSL job description language.]
                  \textbf{Job submission using the xRSL job description language.}}
        ]
 &
 (executable = "run.sh" )
 (arguments = "weka.classifiers.trees.J48" "-t" "weather.arff")
 ("inputfiles" = ("weather.arff" "" ))
 ("stderr" = "stderr" )
 ("stdout" = "stdout" )
 ("gmlog" = "gmlog" )
 ("runtimeenvironment" = "APPS/BIO/WEKA-3.4.10")
 ("runtimeenvironment" = "APPS/BIO/WISE-2.4.1-5")
\end{lstlisting}
\task{The runtime environment names are composed out a directory name, the package name and the version number.}

@@

In addition to using the Janitor together with A-REX, the Janitor can also be used as a standalone command line tool.
The available commands are listed in table~\ref{janitor_commandline_man}.
\begin{table}[!h]
   \begin{center}
        \mycaption{Overview about the available commands in Janitor.}{}
        \label{tab:janitor_commandline_man}
	\begin{tabular}{p{0.5cm}p{2cm}p{11cm}}
	\multicolumn{3}{l}{\textbf{janitor [COMMAND] [JOB-ID] [RTE] \dots}} \\
	\multicolumn{3}{l}{\textbf{Command:}}\\
	&	register			& Registers a job and a set of runtime environments in the Janitor database. Requires the parameters [JOB-ID] and a list of [RTE]s.\\
	&	deploy				& Downloads and installs the desired runtime environments. Requires the name of an already registered [JOB-ID].\\
	&	remove				& Removes the placeholder of the job on the runtime environments. If no more jobs are using the runtime environment and the lifespan of the runtime environment has be expired, the runtime environment can be removed using the \texttt{sweep} command. Requires the [JOB-ID] to be removed.\\
	&					&\\
	&	sweep				& Removes unused runtime environments. No further arguements are required. Using the option \texttt{--force} enforces the removal of all unused runtime environments. Runtime environments having the state FAILED will not be removed.\\
	&	setstate			& Changes the state of a dynamically installed runtime environment. This might be useful in case a runtime environment with a state FAILED shall be removed (new state might be REMOVAL\_PENDING). Requires the argument [STATE] followd by a list of [RTE]s.\\
	&					&\\
	&	search				& Performs a simple search in the catalog and the manually installed runtime environments (\texttt{runtimedir}). Requires no [JOB-ID] nor [RTE]s, but only a list of string to be searched for.\\
	&	list				& Lists all information about jobs, automatically installed runtime environments and manually installed runtime environments. No additional parameters have to be passed.\\
	&	info				& Renders information about a job. Requires the parameter [JOB-ID].\\
	\multicolumn{3}{l}{\textbf{Job id:}}\\
	&					& A unique sequence of numbers. Once Janitor registered a job id, it cannot register a second job having the same job id.\\
	\multicolumn{3}{l}{\textbf{Runtime environments:}}\\
	&					& Runtime environments are defined by a continuous string. The name of valid runtime environment names can be investigated using the \texttt{list} or the \texttt{search} commands. They are defined in the catalog or by the directories and scripts of the \texttt{runtimedir} of the \texttt{grid-manager}.\\
	\end{tabular} 
   \end{center}
\end{table}
The most important commands for the Janitor are \texttt{register}, \texttt{deploy} and \texttt{remove}. To 
register a job along with a set of runtime environments in Janitor, the first command \texttt{register} followed
by a job identifier and a list of runtime environments has to be used.
A job is identified by a sequence of numbers. Runtime environments are specified by a string containing the name as it is defined 
within the Catalog (resp. the runtime directory of the grid-manager).
The command \texttt{deploy} extracts the necessary dependencies of the desired runtime environments to then download and install
the required packages. %How dependecies can are defined will be explained later in the section~\ref{sec:catalog}.

% PROCEED HERE!!!!!!!! !! ! ! !
In order to remove jobs registered in Janitor, the command \texttt{remove}
has to be used.  The command only removes the job entry and the lock
on the runtime environment. If there are no more locks on the runtime
environment it might be deleted for real. The demand to pass a job
number for the removal of a RTE is irritating at first.  This shall
prevent the removal of runtime envrironments that are still being used
by jobs in the system. Instead, the janitor is informed about a job's
termination and is requested to remove the assignment of that job to the
runtime environment. Only those RTEs with no job-assignment are eligible
for being sweeped. RTEs come with an expiry time or the command may be
performed via the command line.

Easy command line examples are provided in Listing~\ref{lst:janitor_example}.

Every command has a certain behaviour for its exit status. The Table~\ref{tab:janitor_commandline_exit_status} lists the possible
outcomes.

>>>>

Janitor can be used either with or without A-REX. In case A-REX is used, installations will be maintained automatically the runtime environments.

@@

Runtime Environments can be specified using the supported job description languages.
Representative two common languages shall be explained at this point: xRSL and JSDL.
Listing~\ref{lst:xrsl_job} shows the xRSL example in which two runtime environments are requested.

\lstsetXRSL
\begin{lstlisting}[
        label=lst:xrsl_job,
        caption={ [Job submission using the xRSL job description language.]
                  \textbf{Job submission using the xRSL job description language.}}
        ]
 &
 (executable = "run.sh" )
 (arguments = "weka.classifiers.trees.J48" "-t" "weather.arff")
 ("inputfiles" = ("weather.arff" "" ))
 ("stderr" = "stderr" )
 ("stdout" = "stdout" )
 ("gmlog" = "gmlog" )
 ("runtimeenvironment" = "APPS/BIO/WEKA-3.4.10")
 ("runtimeenvironment" = "APPS/BIO/WISE-2.4.1-5")
\end{lstlisting}

@@

In addition of using Janitor together with A-REX, Janitor can also be used as a standalone commandline tool.
The available commands are listed in the Table~\ref{tab:janitor_commandline_man}.
\begin{table}[!h]
   \begin{center}
        \mycaption{Overview about the available commands in Janitor.}{}
        \label{tab:janitor_commandline_man}
	\begin{tabular}{p{0.5cm}p{2cm}p{11cm}}
	\multicolumn{3}{l}{\textbf{janitor [COMMAND] [JOB-ID] [RTE] \dots}} \\
	\multicolumn{3}{l}{\textbf{Command:}}\\
	&	register			& Registers a job and a set of runtime environments in the Janitor database. Requires the parameters [JOB-ID] and a list of [RTE]s.\\
	&	deploy				& Downloads and installs the desired runtime environments. Requires the name of an already registered [JOB-ID].\\
	&	remove				& Removes the placeholder of the job on the runtime environments. If no more jobs are using the runtime environment and the lifespan of the runtime environment has be expired, the runtime environment can be removed using the \texttt{sweep} command. Requires the [JOB-ID] to be removed.\\
	&					&\\
	&	sweep				& Removes unused runtime environments. No further arguements are required. Using the option \texttt{--force} enforces the removal of all unused runtime environments. Runtime environments having the state FAILED will not be removed.\\
	&	setstate			& Changes the state of a dynamically installed runtime environment. This might be useful in case a runtime environment with a state FAILED shall be removed (new state might be REMOVAL\_PENDING). Requires the argument [STATE] followd by a list of [RTE]s.\\
	&					&\\
	&	search				& Performs a simple search in the catalog and the manually installed runtime environments (\texttt{runtimedir}). Requires no [JOB-ID] nor [RTE]s, but only a list of string to be searched for.\\
	&	list				& Lists all information about jobs, automatically installed runtime environments and manually installed runtime environments. No additional parameters have to be passed.\\
	&	info				& Renders information about a job. Requires the parameter [JOB-ID].\\
	\multicolumn{3}{l}{\textbf{Job id:}}\\
	&					& A unique sequence of numbers. Once Janitor registered a job id it cannot register a second job having the same job id.\\
	\multicolumn{3}{l}{\textbf{Runtime environments:}}\\
	&					& Runtime environments are defined by a continuous string. The name of valid runtime environment names can be investigated using the \texttt{list} or the \texttt{search} commands. They are defined in the catalog or by the directories and scripts of the \texttt{runtimedir} of the \texttt{grid-manager}.\\
	\end{tabular} 
   \end{center}
\end{table}
The most important commands for Janitor are \texttt{register}, \texttt{deploy} and \texttt{remove}. In order to 
register a job along with a set of runtime environments in Janitor, the first command \texttt{register} followed
by a job identifier and a list of runtime environments has to be used.
A job is identified by sequence of numbers. Runtime environments are specified by a string containing the name as it is defined 
within the catalog (resp. the runtime directory of the grid-manager).
The command \texttt{deploy} extracts the necessary dependcies of the desired runtime environments and then downloads and installs 
the required packages. %How dependecies can are defined will be explained later in the section~\ref{sec:catalog}.

% PROCEED HERE!!!!!!!! !! ! ! !
In order to remove jobs registered in Janitor the command \texttt{remove} has to be used. 
The command only removes the job entry and the lock on the runtime environment. If there are no more locks on the runtime environment
it might be deleted for real.

Easy commandline examples are provided in Listing~\ref{lst:janitor_example}.

Each command has a certain behaviour for its exit status. The Table~\ref{tab:janitor_commandline_exit_status} lists the possible
outcomes.
